%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Education}

%-------------------------------------------------------------------------------
%	SUBSECTION TITLE
%-------------------------------------------------------------------------------
\cvsubsection{Institutions \& Degrees}
%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------
  \cventry
    {MA, ABD, \textit{Cognitive Science, Communication Sciences \& Disorders}} % Degree
    {Northwestern University} % Institution
    {Evanston, IL} % Location
    {2015} % Date(s)
    {
      \begin{cvitems} % Description(s) bullet points
        \item {Qualifying Research Project: Verb Argument Structure Processing in Temporoparietal Cortex}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {BA, \textit{Psychology}} % Degree
    {University of Michigan} % Institution
    {Ann Arbor, MI} % Location
    {2006} % Date(s)
    {}
%---------------------------------------------------------
 \cventry
    {Post-undergraduate coursework, \textit{Psychology and Statistics}} % Degree
    {Grand Valley State University} % Institution
    {Allendale, MI} % Location
    {2008} % Date(s)
    {}

\end{cventries}

%-------------------------------------------------------------------------------
%	SUBSECTION TITLE
%-------------------------------------------------------------------------------
\cvsubsection{Selected Presentations \& Publications}
%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------
  \cventry
    {} % Degree
    {Presentations} % Institution
    {} % Location
    {} % Date(s)
    {
      \vspace{-4mm}
      \begin{cvitems} % Description(s) bullet points
        \item {{\textbf{Kloet, J.}}, \& Barbieri, E. (2014). Treatment of Primary Progressive Aphasia with noninvasive brain stimulation. Invited talk, sponsored by The Roxelyn \& Richard Pepper Department of Communication Sciences and Disorders, the Ruth L. Kirchstein NRSA Institutional Training Grant (T32), and the NIDCD, May 12, Northwestern University, Evanston, IL. }
        \item {{\textbf{Kloet, J.}}, \& Lakey, B. (2009). A Generalizability Theory approach to if\dots, then\dots, situation-behavior relations using Major League Baseball data. Poster presented at Midwestern Psychological Association 81st Annual Meeting, Chicago, IL.}
      \end{cvitems}
    }

%---------------------------------------------------------
\cventry
    {} % Degree
    {Peer-Reviewed Publications} % Institution
    {} % Location
    {} % Date(s)
    {
      \vspace{-4mm}
      \begin{cvitems} % Description(s) bullet points
       \item {Hammer, R., \textbf{Kloet, J.} \& Booth, J. R. (2016). Developmental changes between childhood and adulthood in passive observational and interactive feedback-based categorization rule learning. Developmental Science, 19, 967?981.}
        \item {Galen, L.W., \& \textbf{Kloet, J.} (2011). Personality and Social Integration Factors Distinguishing Nonreligious from Religious Groups: The Importance of Controlling for Attendance and Demographics. Archive for the Psychology of Religion, 33(2), 205-228.}
        \item {Galen, L.W., \& \textbf{Kloet, J.} (2010). Mental well-being in the religious and the non-religious: Evidence for a curvilinear relationship. Mental Health, Religion, \& Culture, 14(7), 673-689.}
      \end{cvitems}
    }

%---------------------------------------------------------
\end{cventries}
